Explorations to Optimize the Parareal Algorithm \\to Solve ODEs in Given Applications

### 2014-12-10 paper.tex
ready to parallelize the process of paper writing

\subsection{Measuring Parallel Performance}

@@

\subsection{Expectations}
TODO WESLEY
\subsection{General Remarks about Resuts}
One of the TODO WESLEY

>>>>

\subsection{Measuring Parallel Performance and Amdahl's Law}

Performance of parallel algorithms are usually measured in terms of 3 different metrics: speedup, strong scalling efficiency and weak scaling efficiency.

@@

\subsection{Expectations}
TODO WESLEY
\subsection{General Remarks about Results}
One of the TODO WESLEY
